### 2019-07-08 2-Chapters/3-Chapter/chapter3.tex
Je fini Ch7 et conclusion demain, je suis épuisé

\paragraph{Read the Docs.}
Since $2017$, we have been using the free web service provided by Read the Docs (\href{https://readthedocs.org/}{\texttt{ReadTheDocs.org}}).
Read the Docs allows to automatically build the documentation after every commit. This allows to regularly check that the library is well formatted and can be imported correctly, as well as keeping the online documentation up-to-date.
Moreover, they offer to host the documentation online, at \href{https://smpybandits.rtfd.io/}{\texttt{SMPyBandits.ReadTheDocs.io}}.
For more details, see \href{https://readthedocs.org/projects/smpybandits/}{\texttt{ReadTheDocs.org/projects/SMPyBandits}}.
%
Since its first use, the service did about 180 builds, and about $10\%$ of them were useful to detect newly introduced issues or bugs in the code.
The build is configured using the \texttt{.readthedocs.yml} file in \SMPyBandits{} main folder, and it builds the documentation in about two minutes.
I have also been building the documentation manually on a weekly basis, to also host it on \href{https://smpybandits.github.io/}{\texttt{SMPyBandits.GitHub.io}} thanks to GitHub pages.
In the last two years, the documentation saw about 11000 unique visits, while the GitHub project have been visited about 4500 unique visits.

@@

The most exciting thing that could happen to our \SMPyBandits{} library would be to see it gaining popularity!
Its documentation has seen already about \href{https://github.com/SMPyBandits/SMPyBandits/graphs/traffic}{$20000$ visits}, \href{https://github.com/SMPyBandits/SMPyBandits/stargazers}{the project on GitHub had $90$ stars} in June $2019$, and based on the features requested and the emails received about it, we counted between $10$ to $20$ researchers in other labs who use or used \SMPyBandits.
While this is a good start, we believe that the library is mature and interesting enough to hope to see it being used by more people.
%
We have submitted a summary paper presenting \SMPyBandits{} \cite{SMPyBanditsJMLR} to the MLOSS track of the Journal of Machine Learning Research (JMLR), and we hope that it will be accepted, as it would give more visibility to this work.
%
As a personal note, I would like to continue working on \SMPyBandits, and implement the most interesting requested features, as well as maintain it, and possibly continue to add recent algorithms by following actively the research in this community.
I would also love to be able to teach a graduate or under-graduate course on reinforcement learning and multi-armed bandits in the next years, and use my library as a support to illustrate such course, as well as practical sessions.

>>>>

\paragraph{Read the Docs.}
Since $2017$, we have been using the free web service provided by Read the Docs (\href{https://readthedocs.org/}{\texttt{ReadTheDocs.org}}).
Read the Docs allows to automatically build the documentation after every commit. This allows to regularly check that the library is well formatted and can be imported correctly, as well as keeping the online documentation up-to-date.
Moreover, they offer to host the documentation online, at \href{https://smpybandits.rtfd.io/}{\texttt{SMPyBandits.ReadTheDocs.io}}.
For more details, see \href{https://readthedocs.org/projects/smpybandits/}{\texttt{ReadTheDocs.org/projects/SMPyBandits}}.
%
Since its first use, the service did about 180 builds, and about $10\%$ of them were useful to detect newly introduced issues or bugs in the code.
The build is configured using the \texttt{.readthedocs.yml} file in \SMPyBandits{} main folder, and it builds the documentation in about two minutes.
I have also been building the documentation manually on a weekly basis, to also host it on \href{https://smpybandits.github.io/}{\texttt{SMPyBandits.GitHub.io}} thanks to GitHub pages.
In the last two years, the documentation saw about 20000 unique visits, while \href{https://github.com/SMPyBandits/SMPyBandits/graphs/traffic}{the GitHub project have been visited about 4500 unique visits}.

@@

The most exciting thing that could happen to our \SMPyBandits{} library would be to see it gaining popularity!
Its documentation has seen already about $20000$ visits, \href{https://github.com/SMPyBandits/SMPyBandits/stargazers}{the project on GitHub had $90$ stars} in June $2019$, and based on the features requested and the emails received about it, we counted between $10$ to $20$ researchers in other labs who use or used \SMPyBandits.
While this is a good start, we believe that the library is mature and interesting enough to hope to see it being used by more people.
%
We have submitted a summary paper presenting \SMPyBandits{} \cite{SMPyBanditsJMLR} to the MLOSS track of the Journal of Machine Learning Research (JMLR), and we hope that it will be accepted, as it would give more visibility to this work.
%
As a personal note, I would like to continue working on \SMPyBandits, and implement the most interesting requested features, as well as maintain it, and possibly continue to add recent algorithms by following actively the research in this community.
I would also love to be able to teach a graduate or under-graduate course on reinforcement learning and multi-armed bandits in the next years, and use my library as a support to illustrate such course, as well as practical sessions.

### 2019-07-08 2-Chapters/5-Chapter/chapter5.tex
Je fini Ch7 et conclusion demain, je suis épuisé

\abstractStartChapter{}%
%
In this chapter, we are interested in a more formal approach to the decentralized learning problem presented in the previous Chapter~\ref{chapter:4}.
We restrict to the easier case of at most $M \leq K$ devices in a network with $K$ channels, that each have data to transmit at every instant, that is they have an activation probability of $p=1$, because it was found very hard to analyze the previously studied IoT network models.
%
We discuss three feedback levels that give variants of the multi-players MAB model previously studied in the literature.
Using a decomposition of the centralized system regret, we start by explaining the intuition about what an efficient decentralized algorithm should do, and then we propose \RandTopM{} and \MCTopM, two new orthogonalization schemes.
Combining them with the \klUCB{} index policy gives order-optimal algorithms, that achieve state-of-the-art performance,
as illustrated by numerical simulations.
We conclude by reviewing different extensions of the multi-players models.

@@

Their proposal is using the \ExpThree{} algorithm from \cite{Auer02NonStochastic} on a combinatorial problem: they consider ``meta'' arms that are affectations of the $M$ players to $M$ distinct arms among the $K$ arms.
As soon as the ``coordinator'' can effectively use one algorithm to decide the arms played by all the $M$ players, they show that the regret will grow as $R_T = \bigO{M^{4/3} K^{2/3} (\log(K))^{1/3} T^{2/3}}$ as shown in Theorem~4.1
(they used $K$ for $M$ the number of players, and $N$ for $K$ the number of arms).
This bound is much worse than the one obtained for the first article \cite{WeiSrivastava18Distributed}, but is more general, and it is much worse than the bound of $\bigO{\sqrt{K T \log(K)}}$ obtained for \ExpThree{} for the single-player adversarial setting in \cite{Auer02NonStochastic}.
Note that this bound in $T^{2/3}$ is of the same order as the one given in \cite{Avner15}, for the \MEGA{} algorithm.
However, we note that the dependency in $M$ is surprisingly better for their result than for the regret upper-bound for \MCTopM-\klUCB{} (while scales in $M^3$ in Theorem~\ref{thm:5:LogarithmicRegret_MCTopMklUCB}).

Moreover, at first sight, this idea of ``meta'' arms implies an exponential blow up in terms of computational and storage cost, as there is ${M \choose K}$ such ``meta arms'', but
the authors provide in Section~4.1 and Lemma~4.1 \cite{AlaturLevyKrause19} an interesting discussion regarding the time efficiency of their proposed algorithm, and they show it can stay polynomial in $M$ and $K$ by leveraging techniques from the Determinental Point Processes (DPP, see \cite{GaBaVa18} for a good review).
%
In this second work also, we can note the poor experimental section, as the proposed algorithm is only compared against the \MusicalChair{} algorithm, in ``easy'' problems (small number of break-points $\Upsilon_T$).
Despite being more complicated than other approaches, their algorithm ``\texttt{C \& P}'' should not be too hard to implement by ourselves, and studying its empirical performance is an interesting future work.

@@

To sum up, we presented in this chapter three variants of Multi-Players Multi-Arm Bandits,
with different levels of feedback being available to the decentralized players, under which we proposed efficient algorithms.
The two easiest models are the ones with sensing information (\ie, for OSA), for which our theoretical contribution improves both the state-of-the-art upper and lower bounds on the regret. In the absence of sensing, we also provide some motivation for the practical use of the interesting \Selfish{} heuristic, a simple index policy based on hybrid indices that are directly taking  into account the collision information.
%
We also reviewed various variants of this model, and for some interesting variants we discussed the related literature, which has proven to be very active in the last two years. For some models, we explained why our approach does not work efficiently without modifications, but we detailed and illustrated how to adapt \MCTopM{} to other settings.
For example, it assumes to know the number of players $M$ before-hand, but we illustrated that previously introduced technique to estimate $M$ can also be applied to our proposal and give satisfactory empirical performances.
Further works would be required to adapt the theoretical analysis to these various extensions.

>>>>

\abstractStartChapter{}%
%
In this chapter, we are interested in a more formal approach to the decentralized learning problem presented of many end-devices accessing the same IoT wireless network
in the previous Chapter~\ref{chapter:4}.
We restrict to the easier case of at most $M \leq K$ devices using a network with $K$ orthogonal frequency channels.
Each device has data to transmit at every instant, that is we restrict to the case of an activation probability of $p=1$, because it was found very hard to analyze the previously studied IoT network models, under the hypothesis of random activation patterns of Chapter~\ref{chapter:4}.
%
We discuss three feedback levels that give variants of the multi-players MAB model previously studied in the literature, and we define the centralized regret as a measure of performance of multi-player bandits algorithms.
%
Using a decomposition of the centralized system regret, we start by explaining the intuition about the expected behavior of any efficient decentralized algorithm, and then we propose \RandTopM{} and \MCTopM, two new orthogonalization schemes.
Combining them with the \klUCB{} index policy gives efficient algorithms, that achieve state-of-the-art performance in terms of their regret,
which is also backed up by numerical simulations.
We conclude by reviewing different extensions of the multi-players models.

@@

Their proposal is using the \ExpThree{} algorithm from \cite{Auer02NonStochastic} on a combinatorial problem: they consider ``meta'' arms that are affectations of the $M$ players to $M$ distinct arms among the $K$ arms.
As soon as the ``coordinator'' can effectively use one algorithm to decide the arms played by all the $M$ players, they show that the regret will grow as $R_T = \bigO{M^{4/3} K^{2/3} (\log(K))^{1/3} T^{2/3}}$ as shown in Theorem~4.1
(they used $K$ for $M$ the number of players, and $N$ for $K$ the number of arms).
This bound is much worse than the one obtained for the first article \cite{WeiSrivastava18Distributed}, but is more general, and it is much worse than the bound of $\bigO{\sqrt{K T \log(K)}}$ obtained for \ExpThree{} for the single-player adversarial setting in \cite{Auer02NonStochastic}.
Note that this bound in $T^{2/3}$ is of the same order as the one given in \cite{Avner15}, for the \MEGA{} algorithm.
However, we note that the dependency in $M$ is surprisingly better for their result than for the regret upper-bound for \MCTopM-\klUCB{} (which scales in $M^3$ in Theorem~\ref{thm:5:LogarithmicRegret_MCTopMklUCB}).

Moreover, at first sight, this idea of ``meta'' arms implies an exponential blow up in terms of computational and storage cost, as there is ${M \choose K}$ such ``meta arms'', but
the authors provide in Section~4.1 and Lemma~4.1 \cite{AlaturLevyKrause19} an interesting discussion regarding the time efficiency of their proposed algorithm, and they show it can stay polynomial in $M$ and $K$ by leveraging techniques from the Determinental Point Processes (DPP, see \cite{GaBaVa18} and references therein for a good introduction).
%
In this second work also, we can note the poor experimental section, as the proposed algorithm is only compared against the \MusicalChair{} algorithm, in ``easy'' problems (small number of break-points $\Upsilon_T$).
Despite being more complicated than other approaches, their algorithm ``\texttt{C \& P}'' should not be too hard to implement by ourselves, and studying its empirical performance is an interesting future work.

@@

To sum up, we presented in this chapter three variants of Multi-Players Multi-Arm Bandits,
with different levels of feedback being available to the decentralized players, under which we proposed efficient algorithms.
The two easiest models are the ones with sensing information (\ie, for OSA), for which our theoretical contribution improves both the state-of-the-art upper and lower bounds on the regret. In the absence of sensing, we also provide some motivation for the practical use of the interesting \Selfish{} heuristic, a simple index policy based on hybrid indices that are directly taking into account the collision information, like in Chapter~\ref{chapter:4}.

We also reviewed various variants of this model and we discussed the related literature, which has proven to be very active in the last two years. For some models, we explained why our approach does not work efficiently without modifications, but we detailed and illustrated how to adapt \MCTopM{} to other settings.
For example, it assumes to know the number of players $M$ before-hand, but we illustrated that a previously introduced technique to estimate $M$ on the run can also be applied to our proposal and give satisfactory empirical performances.
Further works would be required to adapt the theoretical analysis to these various extensions, such as the ``dynamic'' case which allows arrivals or departures of devices, and which is especially interesting for Cognitive Radio applications.
